\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{tabularx}
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
%usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage[cm]{fullpage}
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
%\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
{\centering
		{\Large Ram\'{o}n Dar\'{i}o   Iglesias
	}\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
%\section{Contact Information}

\centering{650.669.7306 | \href{mailto:ramon.d.iglesias@gmail.com}{ramon.d.iglesias@gmail.com}}



%Section: Work Experience at the top
\section{Experience}
\begin{tabularx}{\textwidth}{r|X}

\textsc{01/2015-\emph{Present} } &  \textsc{SunPower}, Richmond, CA \\&\emph{Financial Engineer}\\&\footnotesize{Reduced cost of the residential pricing engine by 80\% and the response time by 90\% by building and migrating to a new pricing engine built in Python and deployed in Amazon Web Services.

Enabled non-programming analysts to run complex financial analyses, and automated the process of cleaning, storing and visualizing existing lease information by building an internal web application using the existing financial code base, writing cleaning scripts and a task/queue system.}\\\multicolumn{2}{c}{} \\

\textsc{07/2014-12/2014} &  \textsc{Stanford University}, Stanford, CA \\&\emph{Graduate Researcher}\\&\footnotesize{
Reduced wind farm construction costs by 6\% by developing, as part of a multidisciplinary team, a method to parametrize construction cost, and optimize wind turbine layout and construction schedule. 

Enabled contractors to visually and quantitatively gauge the risks of working days lost due to high winds by building a web application that predicts the expected number of days lost by month and the best hours of the day to work each month by training a discrete time-inhomogeneous Markov model using past hourly wind data.
}\\\multicolumn{2}{c}{} \\

 %\textsc{06/2013-08/2013} &  \textsc{Project Frog}, San Francisco, CA \\&\emph{Inventory Control Intern}\\&\footnotesize{Coordinated building component deliveries and tracked material inventories for four different school construction sites totaling 17 buildings within a three month schedule.}\\\multicolumn{2}{c}{} \\

%\textsc{06/2012-08/2012} &  \textsc{Steger Bizzell}, Georgetown, TX \\&\emph{Water Utility Modeling Intern}\\&\footnotesize{Modeled a utility company's water and wastewater infrastructure using ArcGIS to provide asset management, demand forecast, and network optimization.}\\\multicolumn{2}{c}{} \\

%\textsc{07/2011-08/2011} &  \textsc{Consorcio Carlo}, Guadalajara, Mexico \\&\emph{Superintendent}\\&\footnotesize{Developed the schedule, procured the required materials, managed the on-site operations, and helped prepare permit applications for a small residential project}\\\multicolumn{2}{c}{} \\

%\textsc{06/2011-07/2011} &  \textsc{Grupo Atelier}, Guadalajara, Mexico \\&\emph{Cost Estimating Intern}\\&\footnotesize{Prepared detailed cost estimates for a range of different house designs of a residential development.}\\\multicolumn{2}{c}{} \\

\end{tabularx}




%Section: Education
\section{Education}
\begin{tabularx}{\textwidth}{r|X}	
 \textsc{09/2012-06/2014} & \textsc{Stanford University} \\ 
& \emph{M.S. in Construction Engineering and Management} \\&\footnotesize{Focus: Multidisciplinary Design Optimization, Virtual Design and Construction, Machine Learning.}\\\multicolumn{2}{c}{} \\

\textsc{08/2007-06/2012} & \textsc{The University of Texas at Austin}\\
& \emph{B.S. in Civil Engineering} \\&\footnotesize{Focus: Risk Analysis, Design Optimization, Building Information Modeling.}\\\multicolumn{2}{c}{} \\
\end{tabularx}













%Section: Scholarships and additional info
\section{Research Experience}
\begin{tabularx}{\textwidth}{r|X}

 \textsc{10/2013-05/2014} &  \textsc{Stanford University}\\&\emph{Wind Farm Layout Optimization}\\&\footnotesize{Enhanced state of the art layout optimization with methods that take into account detailed costs and construction knowledge. Achieved to parametrically create high performing, buildable turbine layouts.}\\\multicolumn{2}{c}{} \\

\textsc{09/2010-05/2011} &  \textsc{The University of Texas at Austin}\\&\emph{Life-Cycle Analysis using Building Information Models}\\&\footnotesize{Explored the current workflow for life-cycle costing and energy modeling, and how building information modeling could improve the process. Concluded with a case study laying out the difficulty of performing useful life-cycle analysis and how proper BIM implementation can streamline the process.}\\\multicolumn{2}{c}{} \\

%\textsc{11/2009-07/2010} &  \textsc{Technical University Munich}\\&\emph{High Performance Concrete Adhesives}\\&\footnotesize{Tested different concrete adhesive when applied to high performance concrete.}\\\multicolumn{2}{c}{} \\

\end{tabularx}




%Section: Scholarships and additional info
\section{Selected Projects}
\begin{tabularx}{\textwidth}{r|X}

\textsc{08/2015-\emph{Present}} &  \textsc{groupstats.io}\\&\emph{Side Project}\\&\footnotesize{Designed the architecture, and built frontend and backend features for  \emph{groupstats.io}, a web application that allows users to visually analyze the dynamics of their Whatsapp chats.}\\\multicolumn{2}{c}{} \\

%\textsc{11/2014-01/2015} &  \textsc{Let's Get Weird}\\&\emph{Startup Weekend}\\&\footnotesize{Built a mobile app to share pictures with nearby people during the peak nightlife hours.}\\\multicolumn{2}{c}{} \\

\textsc{09/2013-04/2014} &  \textsc{Industrialized Construction Studio}\\&\emph{Stanford University}\\&\footnotesize{Helped organized a course investigating the methods, drivers and barriers of industrialized construction through engagement with American and Swedish companies in the form of site visits, lectures, and joint projects.}\\\multicolumn{2}{c}{} \\

% \textsc{11/2013- 12/2013} &  \textsc{Stanford University}\\&\emph{Learning Algorithm for Optimization}\\&\footnotesize{Developed a Naive Bayes based algorithm to accelerate the optimization of Wind Farm Layouts}\\\multicolumn{2}{c}{} \\

%\textsc{03/2011-05/2012} &  \textsc{The University of Texas at Austin}\\&\emph{Modular Steel Frame Optimization}\\&\footnotesize{Developed a model that optimized the spatial arrangement and sizing arrangement of a steel frame modular building.}\\\multicolumn{2}{c}{} \\

%\textsc{04/2010-08/2010} &  \textsc{Technical University Munich}\\&\emph{Risk Based Flood Protection Optimization}\\&\footnotesize{Optimized a flood protection system by balancing the trade-off between mitigation cost and expected cost of failure under different land use scenarios.}\\\multicolumn{2}{c}{} \\

\end{tabularx}







%Section: Skills

\section{Skills}
\begin{tabularx}{\textwidth}{rX}
 \textsc{Languages:}& Spanish (native), English (fluent), German (intermediate)\\ \\ 
\textsc{Technical:}& Python, AWS,  Git, Docker, Revit, Vico, Micrososft Office, AngularJS, Javascript, \LaTeX\\
\end{tabularx}


\end{document}
